\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{fontspec}
\usepackage[compact]{titlesec}

%\setmainfont{FiraSansRegular}

%\addtolength{}{}

\begin{document}

\title{\bf{Curriculum Vitae}}
\author{
  Ross Fenning\\
  Mobile: 07763 616456\\
  e-mail: cv@rossfenning.co.uk
}

\date{\today\footnote{Latest version always available at https://rossfenning.co.uk/}}
\maketitle

\vspace{-0.5cm}

\hrulefill

\section*{Personal Profile}

I am a systems/software engineer who takes holistic approach to
Systems, DevOps and software development and delivery.
This includes all of software development, architecture, continuous delivery,
reducing duplicated effort and the human side of how teams ship changes safely
at pace.

Currently, I am open to both permanent and contract roles that fit the
principal, consultant or staff engineer level.
Permanent salary expectations would be £100k to £150k.
For contract roles, I'd be open to most software
engineering roles with day rate between £500 and £700 outside IR35.
For inside IR35, I would expect day rates towards the higher end of that range.

Areas I've covered as part of working on BBC online have included analytics,
microservices for distributed teams and centralised delivery automation.
I've  also been a driver of reducing overheads and undifferentiated heavy
lifting in how we build, test and deliver our applications.
I prefer to remain able to touch on any technology stack, but my bias would
be towards projects primarily using Python or Java.


\section*{Skills}


\subsection*{Expert}

Agile, Apache HTTP Server, AWS, AWS Cloudformation, BDD, CentOS, Continuous Delivery, Debian, DevOps, Jenkins, Jenkins Pipelines, Kanban, Infrastructure as Code, Linked Data, Maven, nginx, Python, RDF, Red Hat, REST, Systems, TDD, Troposphere, UML

\subsection*{Advanced}

Cucumber, DevOps, Django, Docker, Eclipse Jersey, Elasticsearch, Flask, Git, GNU Make, GNU/Linux, Google BigQuery, Gradle, Java, JAX-RS, LaTeX, MySQL, Node.js, PostgreSQL, Ruby, Scrum, Solr, Spring Boot, SQL, Subversion

\subsection*{Intermediate}

ActiveMQ, FastAPI, GCP, Groovy, Jupyter Notebook, Kubernetes, NumPy, Prolog, RabbitMQ, Redis, Selenium, Soft Systems Methodology, SPARQL, Terraform, Typescript


\vfill

\section*{Work Experience}



\subsection*{Principal Software Engineer at BBC North: 2015-06 to 2022-09}


Role in the Search and Navigation team supporting other engineers where needed
and doing more "hands on" technical work when it comes to prototyping
or in the DevOps and deployment automation domain.

The technical stacks these days are a mix of Java (JAX-RS, Spring Boot, Jersey),
Node.js (Express, some Typescript) and Python (Flask dashboard, Django for
internal tools).
I have contributed significantly to all the Python-based
automation for AWS and CI/CD where some Groovy is used for Jenkins pipelines
as well.

I have also been involved in architectural design and data modelling for
improving our pan-website analytics and work to improve our tracking beyond
simple impressions and clicks, e.g. user engagement tracking and audience
demographics.




\subsection*{Senior Software Engineer at BBC North: 2012-02 to 2015-06}

Enterprise Integration project migrating
        the BBC Search product onto Java microservices using a mix of REST (JAX-RS, Jersey)
        and message-driven architecture (Apache Camel and ActiveMQ). I worked
        on migrating some services to Spring Boot on AWS later on.
        Services were defined via formal BBC processes involving Cucumber and Ruby.



\subsection*{Contract Software Engineer at BBC Cymru Wales: 2010-12 to 2012-02}

The role involved Java business layer services to provide data feeds for
the Home page and also contributions to the PHP/JS front end presentation layer. Also worked on the location search behind BBC Weather using Apache Solr and
building Java REST services around it.



\subsection*{Systems Developer at Cranfield University: 2007-04 to 2010-06}

Systems Developer in the university IT department,
        working on in-house solutions. Most projects were Java web apps
        on Apache Tomcat, connecting with Oracle and Active Directory,
        using Apache Struts framework.



\subsection*{Tester at Transversal Corporation: 2006-02 to 2005-10}

Manual and automation tester for a
web-based software product. Maintained an automated test code in Python that
tested performance of the application as well functionality.



\subsection*{Fundraiser at Tim Lilley Fundraising: 2005-10 to 2006-12}

House to house fundraiser on behalf of Amnesty International.



\subsection*{Tester at Level 5 Networks: 2004-07 to 2004-09}

I tested performance for a new Ethernet interface and its drivers on both Linux and Windows servers.




\section*{Education}



\subsection*{MSc Software Engineering at University of Bradford [2016]}

MSc degree
in Software Engineering and Internet Architecture awarded by Bradford University
run in conjunction with the BBC.



\subsection*{MA Computer Science at University of Cambridge [2005]}

MA (Hons) (Cantab) in Computer Science from the University of Cambridge.




\end{document}
